### 2015-05-27 writing/SNLI paper/corpus.tex
Pre workshopping cleanup.

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Table \ref{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing. The Fleiss $\kappa$ scores in
Table~\ref{kappas} are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

\todo{Update as appropriate (CM)}

>>>>

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Table \ref{validation-stats}. 
Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing. The Fleiss $\kappa$ scores 
(computed over every example with a full five annotations)
are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

\noindent\todo{Update as appropriate (CM)}

### 2015-05-27 writing/SNLI paper/entailment_eval.tex
Update (still prelim) results
Update bibtex
Pre workshopping cleanup.

% TODO(Sam): Can you add these to the Bibtex?
%
%@article{miller1995wordnet,
%  title={{W}ord{N}et: a lexical database for English},
%  author={Miller, George A},
%  journal={Communications of the ACM},
%  volume={38},
%  number={11},
%  pages={39--41},
%  year={1995},
%  publisher={ACM}
%}
%
%@inproceedings{chklovski2004verbocean,
%  title={VerbOcean: Mining the Web for Fine-Grained Semantic Verb Relations.},
%  author={Chklovski, Timothy and Pantel, Patrick},
%  booktitle={EMNLP},
%  year={2004}
%}
%
%@inproceedings{wang2007recognizing,
%  title={Recognizing textual entailment using sentence similarity based on dependency tree skeletons},
%  author={Wang, Rui and Neumann, G{\"u}nter},
%  booktitle={ACL-PASCAL Workshop on Textual Entailment and Paraphrasing},
%  year={2007},
%}

@@

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the RTE baselines -- this is in some sense unsurprising:
  the RTE systems have been tuned on relatively small corpora
  (~1600 examples), whereas a classifier trained on SNLI can make use of
  over two orders of magnitude more data.

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{?} & \t{68} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}

>>>>

@@

% Insights 1: lexicalization helps a bunch
It is interesting to note the substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
In fact, the addition of these features alone allow the classifier to
  outperform the RTE baselines -- this is in some sense unsurprising:
  the RTE systems have been tuned on relatively small corpora
  ($\sim$1600 examples), whereas a classifier trained on SNLI can make use of
  over two orders of magnitude more data.

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{67?} & \t{69?} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}
